%% start of file `template_en.tex'.
%% Copyright 2007 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}
\usepackage{hyperref}

% moderncv themes
\moderncvtheme[grey]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{Joshua}
\familyname{Richer}
%\title{Resumé title (optional)}               % optional, remove the line if not wanted
%\address{170 W 74th St, Apt 1212}{NY, NY 10023}    % optional, remove the line if not wanted
%\mobile{646.926.7840}
\email{joshamosricher@gmail.com}                      % optional, remove the line if not wanted
\extrainfo{https://www.linkedin.com/in/joshuaar}
 % optional, remove the line if not wanted
%\photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{"They can kill you, but the legalities of eating you are quite a bit dicier" - David Foster Wallace}                 % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Profile}
I'm a scientist with training in \textbf{computer science, statistics, and biology}. I've worked with high dimensional data on clustering, classification, modeling and software engineering problems in both academic and industry settings. I seek and would thrive in an interdisciplinary, team oriented and technical environment. See github (\link{https://github.com/joshuaar}) or linkedin (\link{https://linkedin.com/in/joshuaar}) for more details.

\section{Skills}
\cventry{}{Analytical Skills}{}{Experience in \textbf{supervised and unsupervised machine learning}, genomics data analysis, high dimensional data, multivariate and nonparametric statistics, data visualization in R and Python, schema design, object priented programming, functional programming, web development}{}{}
\cventry{}{Languages}{}{Python, R, Scala, Java, C++, Javascript}{}{}
\cventry{}{Software/Libraries}{}{Linux, ElasticSearch, Apache Spark, Apache Lucene, Vim, Git, Illustrator}{}{}

\section{Experience}

\cventry{12.2014-Present}{Orion Health}{Software Engineer}{Scottsdale, AZ}{}{
Designing analytics systems using \textbf{Spark, Scala and Elasticsearch} to solve population health problems.
\newline
- Designed and wrote Spark Jobs for \textbf{indexing millions of patient records} in a data warehouse based on Elasticsearch.
\newline
- Designed, performed and reported on a \textbf{pilot study} aimed at predicting \textbf{hospital readmission risk} given certain clinical variables found in claims data.
\newline
- Present machine learning topics to a group of engineers.
}

\cventry{01.2014-12.2014}{USDA Agricultural Research Service}{Bioinformatics Specialist}{Maricopa, AZ}{}{
\textbf{Fixed-term appointment} to set up and ran a small informatics core facility focusing primarily on \textbf{RNA-Seq transcriptomics} in insects. 
\newline
- Built a \textbf{web interface} exposing tools for parallel processing of genomics data to research scientists.
\newline
- \textbf{Designed an analysis pipeline} available on Galaxy for de-novo transcriptome assembly, annotation, searching and visualization. Used by three participating research groups.
\newline
- Support and parallelization of FORTRAN code for radiative transfer atmospheric models.
\newline
- Wrote XML and cheetah templates for use with the Galaxy bioinformatics suite. 
}

\cventry{08.2010-12.2014}{Biodesign Institute}{Research Associate}{Tempe, AZ}{}{
Conducted research projects involving high density peptide microarrays. I designed experiments, \textbf{algorithms and software} for the Immunosignature technology (\link{http://en.wikipedia.org/wiki/Immunosignature}).  
\newline
- Wrote non-parametric (bootstrapping) validation procedures for a an immunosignature based Dengue Fever diagnostic. Includes \textbf{feature selection, SVM classification, cross validation, ROC analysis} and visualization. I packaged this into a command line application which became standard protocol in the lab.
\newline
- Designed and tested a system for rapidly mapping B-Cell epitopes from human sera and monoclonal antibodies. Includes a novel \textbf{statistical algorithm} for epitope determination from noisy sequence data.
\newline
- Designed and built a rapid pattern search engine for biological sequences using \textbf{Apache Lucene and Scala}. It is over 100x faster than naive methods, and useful for identifying peptide motifs in large sequence databases. Includes \textbf{trigram index, pattern compiler, web interface}.
\newline
}

\cventry{2009-2010}{Entech}{Quality Control Engineer}{White Pigeon, MI}{}{
Directed quality control for a recycling plant specializing in tire rubber for artificial turf, molding and extrusion.
\newline
- Built and supported a database for QC results with \textbf{nightly backups to offsite storage}.
\newline
- Wrote procedures creating formatted reports for management.
\newline
- Technologies used: PostgreSQL, Python, Excel
\newline
- Ensured data and product samples were available and accurate, which was important for occasional disputes over quality.
}

\cventry{01.2009-07.2009}{University of Notre Dame}{Research Visitor}{Notre Dame, IN}{}{
Research internship at UND in the lab of Dr. Paul Helquist. Synthesized TSA analogs for treatment of Niemann-Pick disease resulting in two co-authored papers in peer reviewed journals.
}

\section{Education}
\cventry{2010-2014}{Arizona State University, Ira. A. Fulton School of Engineering}{Ph.D, Biological Design (conc. Bioinformatics)}{}{Tempe, AZ}{}
\cventry{2005-2009}{Goshen College}{B.A, Chemistry, Mol. Biology}{}{Goshen, IN}{}
\cventry{}{Quantitative Coursework (Selected)}{}{}{}{
- Nonparametric Statistics
\newline
- Linear Regression
\newline
- Statistical Computing
\newline
- Data Structures and Algorithms
\newline
- Theoretical Computer Science
\newline
- Operating Systems
\newline
- Assembly Language Programming
}

% PUBLICATIONS
\nocite{mcp,dengue,usda,euro,notredame}
\bibliographystyle{unsrt}
\bibliography{resume}

\closesection{}                   % needed to renewcommands
\renewcommand{\listitemsymbol}{-} % change the symbol for lists

% Publications from a BibTeX file

\section{Contact}
\cventry{Phone}{630-319-2073}{}{}{}{}
\cventry{Email}{joshamosricher@gmail.com}{}{}{}{}
\cventry{Email (work)}{josh.richer@orionhealth.com}{}{}{}{}

\end{document}

%% end of file `template_en.tex'.
